NGO Crackdowns and Philanthropy

### 2018-07-16 03_additional-analysis.Rmd
Use safesite

```{r load-libraries-data, warning=FALSE, message=FALSE}
# Unload all the already-loaded packages because R Markdown websites *don't* knit 
# each Rmd in a separate environment: https://github.com/rstudio/rmarkdown/issues/1326
#
# This means that here::here() and lubridate::here() will conflict becuase **here**
# has already been loaded in previous scripts
# 
# Stupid bleeding environments
# https://github.com/andrewheiss/rmarkdown-website-envs-orig
if (isTRUE(getOption('knitr.in.progress')) & !is.null(names(sessionInfo()$otherPkgs))) {
  invisible(suppressWarnings(sapply(paste0("package:", names(sessionInfo()$otherPkgs)),
                                    detach, character.only = TRUE)))

  # THIS IS SO EVIL AND AWFUL BUT NECESSARY BECAUSE STUFF HAPPENS IN PREVIOUS
  # FILES THAT BREAK THIS FILE WHEN IT IS KNIT AS PART OF AN RMARKDOWN WEBSITE
  #
  # DON'T TELL JENNY BRYAN
  rm(list = ls())
  # AHHH THE HORROR
}

# Load libraries again
library(tidyverse)
library(magrittr)
library(rstan)
library(rstanarm)
library(broom)
library(glue)
library(ggstance)
library(ggridges)
library(grid)
library(gridExtra)
library(Gmisc)
library(patchwork)
library(pander)
library(scales)
library(huxtable)
library(lubridate)
library(modelr)
library(ipumsr)
library(here)

>>>>

```{r load-libraries-data, warning=FALSE, message=FALSE}
# Load libraries
library(tidyverse)
library(magrittr)
library(rstan)
library(rstanarm)
library(broom)
library(glue)
library(ggstance)
library(ggridges)
library(grid)
library(gridExtra)
library(Gmisc)
library(patchwork)
library(pander)
library(scales)
library(huxtable)
library(lubridate)
library(modelr)
library(ipumsr)
library(here)

### 2018-07-16 index.Rmd
Use safesite

---
title: "NGO Crackdowns and Philanthropy"
author: "Suparna Chaudhry and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
---

>>>>

---
title: "NGO Crackdowns and Philanthropy"
author: "Suparna Chaudhry and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
site: safesite::safesite
---
